Cyclone: Fault Tolerance Middleware for NVM Clusters

### 2016-05-04 paper/paper.tex

This paper presents Cyclone - fault tolerance middleware that exposes a
replicated and durable heap. This heap can be directly manipulated using loads and
stores. Cyclone provides both failure atomicity as well as
strongly consistent replication when updates to the heap are enclosed in
software transactions thereby giving strong guarantees to programmers
with minimal effort on their part. Under the hood Cyclone decouples modification
of local persistent memory from replication to maximize performance. In
addition, unlike traditional systems that provide strong replication, Cyclone
does require programs to be provisioned for checkpoints since NVM is directly
manipulated by programmers and therefore up to date till the last executed
transaction. Instead, Cyclone provides a novel NVM copy mechanism to bring up
new nodes added to the cluster.

\end{abstract}

>>>>

This paper presents Cyclone - fault tolerance middleware that exposes a
replicated and durable heap. This heap can be directly manipulated using loads and
stores. Cyclone provides both failure atomicity as well as
strongly consistent replication when updates to the heap are enclosed in
software transactions thereby giving strong guarantees to programmers
with minimal effort on their part. Under the hood Cyclone decouples modification
of local persistent memory from replication to maximize performance. Unlike
traditional systems that provide strong replication, the ``in-memory'' image is
persistent and there is no need for checkpoints - except when new replicas are
added. In addition linearizable reads can be directly executed without the need to
combine pending updates from a log.
\end{abstract}
